---
title: "Main Notebook"
output: html_notebook
---


###Step 0: Prepare all needed packages
```{r}
list.of.packages <- c("data.table","FeatureHashing","xgboost","dplyr","Matrix","caret","randomForest")
new.packages <- list.of.packages[!(list.of.packages %in% installed.packages()[,"Package"])]
if(length(new.packages))
  {
   install.packages(new.packages)
  }

library(data.table)
library(FeatureHashing)
library(xgboost)
library(dplyr)
library(Matrix)
```

###Step 1: Data processing: Turn category values into numeric values

The process is in DOC file: data_processing.Rmd and data_processing_uniquea_same.Rmd ang the results is in Output links(Since the the limit size of file is 25MB)
```{r}
train_num<- fread("../output/train_num.csv") %>% as.data.frame()
train_num_runique<- fread("../output/train_num_runique.csv") %>% as.data.frame()
```

###Step 1: Models



```{r}
source("/Users/linhan/Desktop/fall2017-project5-proj5-grp3/lib/xgboost.R")
```

```{r, warning=FALSE}
run.xgb<- TRUE
if(run.xgb){
 system.time(xgb(train_num_runique, K=5))
}
```





Part 1: Model Selction ######Need to train the best parameters(plz write thsi process into function)

Model1: SVM

Model2: Logistic Regression

Model3: Random Forest

Model4: GBM

Model5: LightGBM

Model6: Xgboost

Model7: Neural Network

Part 2: Feature Selection

1. Feature Importance

2. PCA

3.Bag of words techniques

Part 3: Retrain model
